---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# An R interface to the Predictit API
This package provides an interface to the Predictit public API (). License to use data made available via the API is for non-commercial use and PredictIt is the sole source of such data. In addition to providing a wrapper to retrieve market data, this package includes visualization and analysis functions.

## Installation

You may install the stable version from CRAN, or the development version using *remotes*:
```{r}
# install from CRAN
install.packages('DT')

# or the development version
remotes::install_github('danielkovtun/predictit')

```

## Usage

To start off, try pRedictit::get_predictit_market_data() to return a tbl containing bid and ask data for all Predictit markets:

```{r}
library(pRedictit)
get_predictit_market_data()
```

Alternatively, to return an interactive htmlwidget (DT::datatable) table containing HTML formatted market data:

```{r}
pRedictit::get_predictit_markets_table()
```
